### 2023-09-20 main.tex
jkl

    		\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\right. 
    		\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e^{\varphi_{1},\ldots,\varphi_{L}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.

@@

    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{\tau_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}

@@

    		\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}} \right\}

@@

	\varphi_{x}(q_{1},\ldots,q_{L})=\begin{cases}
		\tau_{x}\qquad &\text{if}\quad x\notin\{q_{1},\ldots,q_{L}\}\\

@@

The dependence of $\varphi_{x}(q_{1},\ldots,q_{L})$ with respect to $q_{1},\ldots,q_{L}$ is usually understood for the sake of notation.

@@

    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e^{\varphi_{1},\ldots,\varphi_{L}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.

@@

    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}\beta_{\tau_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.

@@

    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}

@@

    	\sum_{q_{1},\ldots,q_{L+1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L+1}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}} \right\}

@@

\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}

@@

  \ldots+\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\;\text{if}\;i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}

Therefore, we have that 
\begin{equation}\label{ABS_intermediate}
	\begin{split}
		\Psi^{'}(\bm{\tau})&=(\mathcal{S}_{2}^{-1})_{\bm{\tau}}^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\varphi_{1},\ldots,\varphi_{L})\beta_{q_{1}}\\&+
		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\varphi_{1},\ldots,\varphi_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}
	\end{split}
\end{equation}
For a fixed configuration $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$, using equation \eqref{ResulsBasis} and observing that 
\begin{equation}
  \left(1+\sum_{j=y}^{L}\delta_{s_{j},1}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{y},1})\right)
\end{equation}
we obtain 
    \begin{equation}
\Psi^{''}(\bm{\tau})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{y},1})\right)\right)^{1-\delta_{\tau_{y},1}}
\end{equation}
Introducing
\begin{equation}
	c_{y}=(1-\delta_{\tau_{y},1}) \qquad \forall y\in \{1,\ldots L\}
\end{equation}
and replacing $\Psi^{'}(\bm{\tau})$ computed above in \eqref{ABS_intermediate} we obtain

@@

In this section we write a formula for the stationary steady state correlations between $m$- points of the chain, each of them occupied by a non empty species, i.e. a species with label from $1$ to $N-1$. This is motivated by interest of understanding how actual particles of the chain are correlated among each others and also because the holes depends on the occupation of all other species, as a consequence of the constraint $n_{N}^{x}=\nu-\sum_{b=1}^{N-1}n_{b}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$. Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{y}=(y_{1},\ldots,y_{m})$, such that $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$. In each of these points there is a particle of species $a_{i}\in \{1,\ldots,N-1\}$. Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by

@@

		\langle n^{y_{1}}_{a_{1}}\cdots n^{y_{m}}_{a_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
			f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})

@@

\langle n^{y_{1}}_{a_{1}}\cdots n^{y_{m}}_{a_{m}}\rangle_{\text{stat}}=&

@@

f(L,c_{1},\ldots,c_{m})\prod_{q=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})\right)\\

@@

f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})

@@

\langle n^{y_{1}}_{a_{1}}\cdots n^{y_{m}}_{a_{m}}\rangle_{\text{stat}}=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}\\
=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{q}^{t_{q}}\beta_{q}^{1-t_{q}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})

@@

where $\hat{\bm{\xi}}=\sum_{i=1}^{m}\delta_{a_{i}}^{x_{i}}$.  
\paragraph{Proof of formula \eqref{exactCorrelations}} Consider $m$ particles of non-empty types $a_{i}\in\{1,\ldots,N-1\}$ in positions $y_{i}\in\{1,\ldots,L\}$ for all $i=1,\ldots,m$. We aim to compute the non-equilibrium stationary state correlation $\langle n_{a_{1}}^{y_{1}}\cdots n_{a_{m}}^{y_{m}} \rangle_{stat}$. By using duality, we showed in \eqref{CorrelationByABS-prob} that
 	\langle n_{a_{1}}^{y_{1}}\cdots n_{a_{m}}^{y_{m}} \rangle_{stat}=\langle\hat{\bm{\xi}}\rangle_{stat,dual}
Using formula \eqref{ABS} for a configuration where all $\tau_{y_{i}}=a_{i}$  for $i=1,\ldots,m$ and $\tau_{j}=N$ for $j\in\{1,\ldots,L\}\setminus \{y_{1},\ldots,y_{m}\}$, we obtain 

>>>>

    		\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{1},\ldots,\varphi_{L}^{1}}\beta_{\tau_{q_{1}}}\right. 
    		\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e^{\varphi_{1}^{2},\ldots,\varphi_{L}^{2}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.

@@

    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{\tau_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L-1},\ldots,\varphi_{L}^{L-1}}

@@

    		\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L},\ldots,\varphi_{L}^{L}} \right\}

@@

	\varphi_{x}^{i}(q_{1},\ldots,q_{i})=\begin{cases}
		\tau_{x}\qquad &\text{if}\quad x\notin\{q_{1},\ldots,q_{i}\}\\

@@

where $i\in\{1,\ldots,L\}$. The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation.

@@

    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{1},\ldots,\varphi_{L}^{1}}\beta_{\tau_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e^{\varphi_{1}^{2},\ldots,\varphi_{L}^{2}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.

@@

    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1}^{1},\ldots,\varphi_{L+1}^{1}}\beta_{\tau_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1}^{2},\ldots,\varphi_{L+1}^{2}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.

@@

    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1}^{L},\ldots,\varphi_{L+1}^{L}}

@@

    	\sum_{q_{1},\ldots,q_{L+1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L+1}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1}^{L+1},\ldots,\varphi_{L+1}^{L+1}} \right\}

@@

\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{1},\ldots,\varphi_{L}^{1}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{2},\ldots,\varphi_{L}^{2}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}

@@

  \ldots+\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\;\text{if}\;i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L},\ldots,\varphi_{L}^{L}}

Therefore, we have that 
\begin{equation}\label{ABS_intermediate}
	\begin{split}
		\Psi^{'}(\bm{\tau})&=(\mathcal{S}_{2}^{-1})_{\bm{\tau}}^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\varphi_{1}^{1},\ldots,\varphi_{L}^{1})\beta_{q_{1}^{1}}\\&+
		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\varphi_{1}^{2},\ldots,\varphi_{L}^{2})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}
	\end{split}
\end{equation}
For a fixed configuration $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$, using equation \eqref{ResulsBasis} and observing that 
\begin{equation}
  \left(1+\sum_{j=y}^{L}\delta_{\tau_{j},N}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{y},N})\right)
\end{equation}
we obtain 
    \begin{equation}
\Psi^{''}(\bm{\tau})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{y},N})\right)\right)^{1-\delta_{\tau_{y},N}}
\end{equation}
Introducing
\begin{equation}
	c_{y}=(1-\delta_{\tau_{y},N}) \qquad \forall y\in \{1,\ldots L\}
\end{equation}
and replacing $\Psi^{'}(\bm{\tau})$ computed above in \eqref{ABS_intermediate} we obtain

@@

In this section we write a formula for the stationary steady state correlations between $m$- points of the chain, each of them occupied by a non empty species, i.e. a species with label from $1$ to $N-1$. This is motivated by interest of understanding how actual particles of the chain are correlated among each others and also because the holes depends on the occupation of all other species, as a consequence of the constraint $n_{N}^{x}=\nu-\sum_{b=1}^{N-1}n_{b}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$. Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{y}=(y_{1},\ldots,y_{m})$, such that $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$. In each of these points there is a particle of species $s_{i}\in \{1,\ldots,N-1\}$. Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by

@@

		\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
			f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})

@@

\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=&

@@

f(L,c_{1},\ldots,c_{m})\prod_{q=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})\right)\\

@@

f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})

@@

\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\\
=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})

@@

where $\hat{\bm{\xi}}=\sum_{i=1}^{m}\delta_{s_{i}}^{y_{i}}$.  
\paragraph{Proof of formula \eqref{exactCorrelations}} Consider $m$ particles of non-empty types $s_{i}\in\{1,\ldots,N-1\}$ in positions $y_{i}\in\{1,\ldots,L\}$ for all $i=1,\ldots,m$. We aim to compute the non-equilibrium stationary state correlation $\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}} \rangle_{stat}$. By using duality, we showed in \eqref{CorrelationByABS-prob} that
 	\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}} \rangle_{stat}=\langle\hat{\bm{\xi}}\rangle_{stat,dual}
where $\langle\hat{\bm{\xi}}\rangle_{stat,dual}$ we have denoted the stationary state of the dual process starting from the configuration $\hat{\bm{\xi}}$. 
Using formula \eqref{ABS} for a configuration where all $\tau_{y_{i}}=s_{i}$  for $i=1,\ldots,m$ and $\tau_{j}=N$ for $j\in\{1,\ldots,L\}\setminus \{y_{1},\ldots,y_{m}\}$, we obtain 
